\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-21 doc/sw-system.tex
Added a sentence about 0.95 threshold, closes #146

We first quantify the performance of the \SW system in terms of the recovery of
the training set images. At \StageOne, this set contained around 5712 simulated
lenses, and 450 duds; at \StageTwo, we used 152 images of simulated lenses and
201 duds selected as \StageOne false positives (\Sref{sec:design:stages:two}).
\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
curves for \cfhtls \StageOne and \StageTwo. These plots show the true positive
rate (TPR, the number of sims correctly detected divided by the total number of
sims in the training set), and the false positive rate (FPR, the number of duds
incorrectly detected  divided by the total number of duds in the training set), both
for a given sample of detections defined by a particular probability threshold,
which varies along the curves.  In both stages, these curves show that true
positive rates of  around 90\% were achieved, at very low false positive rates.

For comparison we show the results of an analysis where the classifications of
training images were ignored, and the agents' confusion matrix elements
were instead all simply assigned initial values of 0.75
which then remained constant. This set-up emulates a
very simple unweighted voting scheme, where all classifications are treated
equally.  In this case, the TPR remains under 80\% in \StageOne and 60\% in
\StageTwo, thus illustrating the benefit of including training images and
allowing the agents to learn via their Bayesian updates.

When the agents are allowed to update their confusion matrices, the choice of
initial confusion matrix is not very important: the same 0.75 initial values
applied to normal, learning agents resulted in only a slightly lower TPR than
the default case.

The dot-dashed curves show the results from the offline analysis. At \StageOne the
results are very similar to the online version that was actually run (solid
line). However, at \StageTwo there is marginal evidence of there being greater
benefit to doing the analysis offline (\Sref{sec:swap:offline}).
Over 85\% TPR is achieved at zero FPR in the offline analysis , while if one is
willing to accept a false positive rate of 5\%, the true positive rate rises to
over 95\%, showing that some of the sims that were missed in the online analysis
may be being recovered by doing the analysis offline. (The same is true at
\StageOne, but to a lesser extent.) One interpretation for this result (if it holds up)
would be that the offline analysis, by using each agent's entire history, is
making less noisy probability estimates.

Assuming Poisson statistics for the
fluctuations in the numbers of recovered lenses, the uncertainty in the measured
\StageTwo TPR values is around 8\%, but the online and offline samples are
highly correlated, such that the uncertainty on the {\it difference} between the ROC
curves is somewhat less than this. Still, a larger validation set is needed to
test these algorithmic choices more rigorously. At \StageOne, high TPR can be
measured to better than 1\%.

>>>>

We first quantify the performance of the \SW system in terms of the recovery of
the training set images. At \StageOne, this set contained around 5712 simulated
lenses, and 450 duds; at \StageTwo, we used 152 images of simulated lenses and
201 duds selected as \StageOne false positives (\Sref{sec:design:stages:two}).
\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
curves for \cfhtls \StageOne and \StageTwo. These plots show the true positive
rate (TPR, the number of sims correctly detected divided by the total number of
sims in the training set), and the false positive rate (FPR, the number of duds
incorrectly detected  divided by the total number of duds in the training set), both
for a given sample of detections defined by a particular probability threshold,
which varies along the curves.  In both stages, these curves show that true
positive rates of  around 90\% were achieved, at very low false positive rates.
The probability threshold that was used for retirement during the \StageOne online analysis
was 0.95; this point is marked with a star on each curve.
This turned out to be close to optimal (although a better approach would be to
keep track of the ROC curve as the survey progressed!).

For comparison we show the results of an analysis where the classifications of
training images were ignored, and the agents' confusion matrix elements
were instead all simply assigned initial values of 0.75
which then remained constant. This set-up emulates a
very simple unweighted voting scheme, where all classifications are treated
equally.  In this case, the TPR remains under 80\% in \StageOne and 60\% in
\StageTwo, thus illustrating the benefit of including training images and
allowing the agents to learn via their Bayesian updates.
When the agents are allowed to update their confusion matrices, the choice of
initial confusion matrix is not very important: the same 0.75 initial values
applied to normal, learning agents resulted in only a slightly lower TPR than
the default case.

The dot-dashed curves show the results from the offline analysis. At \StageOne the
results are very similar to the online version that was actually run (solid
line). However, at \StageTwo there is marginal evidence of there being greater
benefit to doing the analysis offline (\Sref{sec:swap:offline}).
Over 85\% TPR is achieved at zero FPR in the offline analysis , while if one is
willing to accept a false positive rate of 5\%, the true positive rate rises to
over 95\%, showing that some of the sims that were missed in the online analysis
may be being recovered by doing the analysis offline. (The same is true at
\StageOne, but to a lesser extent.) One interpretation for this result (if it holds up)
would be that the offline analysis, by using each agent's entire history, is
making less noisy probability estimates. This could be consistent with
other citizen science/crowdsourcing projects where,
in the absence of high quality information about classifiers,
sophisticated strategies tend to under-perform naive but simpler
ones \citep{Waterhouse} (although we note that this rule of thumb seems not to extend
to simple voting in this case!).

Assuming Poisson statistics for the
fluctuations in the numbers of recovered lenses, the uncertainty in the measured
\StageTwo TPR values is around 8\%, but the online and offline samples are
highly correlated, such that the uncertainty on the difference between the ROC
curves is somewhat less than this.
Still, a larger validation set is needed to
test these algorithmic choices more rigorously. At \StageOne, high TPR can be
measured to better than 1\%.
